The Adaptive Multi-scale Simulation Infrastructure - Design and Application

### 2016-01-05 doc/articles/amsi_biotissue/paper.tex
paper work

Often the subset(s) of the domain associated with the tertiary scale(s) are locations in the engineering domain where the impact of the tertiary scales has the most impact on the engineering scale simulation, in order to leverage the most power from the multi-scale approach.

@@

\subsection{Soft Tissue Simulation}\label{biotissue}
The Biotissue code is a multi-scale simulation of soft organic tissues, consisting of an engineering-scale simulation using the finite element method, and a micro-scale quasistatics force-balance simulation. The Cauchy Momentum Balance Equation for a body in static equilibrium is used as the governing equation for the global simulation. Specific quantities needed to compute the elemental tangent stiffness matrices are instead supplied by the micro-scale force-balance simulations, which occur at each numerical integration point in the engineering-scale mesh \ref{biotissue_hierarchy}.

@@

Thus the simulation as a whole is essentially doubly nonlinear, as during each engineering-scale Newton iteration every micro-scale RVE must undergo a full Newton-Raphson convergence process.

\section{Results}\label{results}
The biotissue simulation was run on the AMOS BG/Q machine housed at the CCI facilities. Both strong and weak scaling studies were conducted up to an eighth of the total machine core count, or 16384 cores. The ratio of macro-scale to micro-scale assigned processes was held near 1:128, though the total core count was kept as an integer power of 2 in order for the SLURM job scheduler to submit the jobs to the compute nodes in a timely manner. The precise calculation used to determine macro and micro ratio is given by 
$$ 
num_macro = N 
num_cores = N*128
num_micro = num_cores - N
$$
thus as the number of cores assigned to the macro-scale computation scales, the ratio approaches 1:128.

@@

Weak scaling.

Strong scaling.

@@

\section{Future Work}\label{future_work}

Work on scale-balancing is ongoing for the biotissue test problem. Using this work as a basis, a set of algorithms to provide support for more general scale-balancing operations will be developed and packaged into amsi.

>>>>

Often the subset(s) of the domain associated with the tertiary scale(s) are areas of the engineering domain where the impact of the tertiary scales has the most impact on the engineering scale simulation, in order to leverage the most power from the multi-scale approach.

@@

\subsection{Soft Tissue Simulation}\label{biotissue}
The Biotissue code is a multi-scale simulation of soft organic tissues, consisting of an engineering-scale simulation using the finite element method, and a micro-scale quasistatics force-balance simulation. The Cauchy Momentum Balance Equation for a body in static equilibrium is used as the governing equation for the macro-scale simulation. 
%
\begin{align}
\nabla \cdot \pmb{\sigma} =& \; 0 \text{ in } \Omega \label{momentum_balance} \\
\pmb{\sigma} \cdot \pmb{n} =& \; \pmb{t} \text{ on } \partial \Omega \nonumber
\end{align}
%
Specific quantities needed to compute the elemental tangent stiffness matrices and force vectors are instead supplied by the micro-scale force-balance simulations, which occur at each numerical integration point in the engineering-scale mesh \ref{biotissue_hierarchy}.

@@

Thus the simulation as a whole has two Newton-Raphson convergence operations occurring. During each macro-scale Newton iteration every micro-scale RVE must undergo a full Newton-Raphson convergence process.

\section{Results}\label{results}
The biotissue simulation was run on the AMOS BG/Q machine housed at the CCI facilities. Both strong and weak scaling studies were conducted up to an eighth of the total machine core count, or 16384 cores. The ratio of macro-scale to micro-scale assigned processes was held near 1:128, though the total core count was kept as an integer power of 2 in order for the SLURM job scheduler to submit the jobs to the compute nodes in a timely manner. The precise calculation used to determine macro and micro ratio is given by 
%
num_macro = N 
num_cores = N*128
num_micro = num_cores - N
%
thus as the number of cores assigned to the macro-scale computation increases, the ratio approaches 1:128.

@@

Weak scaling results...

Strong scaling results...

@@

Could include utilization/idle time metrics, but those are far more relevant to the load balancing paper...

\section{Conclusions and Future Work}\label{future_work}

The Adaptive Multi-scale Simulation Infrastructure provides a valuable set of tools to facilitate the implementation and execution of multi-scale simulations without imposing restrictions on the application developer. Usage of the core operations of the amsi libraries does not require adherence to a specific set of interfaces nor usage of an abstract modeling language, which complicate inclusion of legacy components into multi-scale simulations.
